Asymptotic and Numerical Solution for Electrokinetic Flow Around a Spherical Particle

### 2012-10-17 notes/thesis/main.tex
Rename thesis main LATEX file.

We consider a spherical particle.
The chemical properties of the particle's surface $\mathcal{S}$ (defined at $r=1$ 
with normal $\bn = \brhat$), determine the boundary conditions on $\mathcal{S}$.
We consider the following scenarios:
\subsubsection{Ion-exchanger \cite{yariv2010migration}}
We assume high conductance of the particle (yielding a uniform electric potential),
zero slip, anion impermeability, cation selectivity 
(with fast Butler-Volmer\cite{bard2000book} kinetics
$\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$):
\begin{equation}
\begin{array}{cccc}
\varphi = \cV, &
\bv = \bzero, &
\bn \cdot \bj_- = 0, &
c_+ = \gamma,
\end{array}
\end{equation}
where $\gamma$ is the ratio between the cationic concentration on the surface and the cationic
concentration in the fluid bulk and $\cV$ is an unknown constant electric potential at
the ion-exchanger surface.

\subsubsection{Inert particle \cite{schnitzer2012surface}}
We assume constant surface charge
zero slip and ion impermeability:
\begin{equation}
\begin{array}{cccc}
\bn \cdot (\bnabla \varphi - \chi \bnabla \varphi_s) = \delta^{-1} \sigma, &
\bv = \bzero, &
\bn \cdot \bj_\pm = 0,
\end{array}
\end{equation}
where $\chi$ is the ratio between the dielectric constants of the 
particle and the fluid.

@@

Each discrete variable is located with respect of its cell as follows:
$\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
using an all-centered grid, whereas $\bV$ is represented by its values at cell 
boundaries, using a staggered grid:
\begin{equation}
\begin{array}{ccccc}
\varPhi^h_{[i,j]} = \varPhi(\bar{r}_i, \bar{\theta}_j), &
C^h_{[i,j]} = C(\bar{r}_i, \bar{\theta}_j), &
P^h_{[i,j]} = P(\bar{r}_i, \bar{\theta}_j). &
V_r^h{}_{[i,j]} = V_r(r_i, \bar{\theta}_j), &
V_\theta^h{}_{[i,j]} = V_\theta(\bar{r}_i, {\theta}_j).
\end{array}
\end{equation}

>>>>

We consider a spherical particle.
The chemical properties of the particle's surface $\mathcal{S}$ (defined at $r=1$ 
with normal $\bn = \brhat$), determine the boundary conditions on $\mathcal{S}$.
We consider the following scenarios:
\subsubsection{Ion-exchanger}
Following \cite{yariv2010migration}, we assume high conductance of the particle (yielding a uniform electric potential),
zero slip, anion impermeability, cation selectivity 
(with fast Butler-Volmer\cite{bard2000book} kinetics
$\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$):
\begin{equation}
\begin{array}{cccc}
\varphi = \cV, &
\bv = \bzero, &
\bn \cdot \bj_- = 0, &
c_+ = \gamma,
\end{array}
\end{equation}
where $\gamma$ is the ratio between the cationic concentration on the surface and the cationic
concentration in the fluid bulk and $\cV$ is an unknown constant electric potential at
the ion-exchanger surface.

\subsubsection{Inert particle}
Following \cite{schnitzer2012surface}, we assume constant surface charge
zero slip and ion impermeability:
\begin{equation}
\begin{array}{cccc}
\bn \cdot (\bnabla \varphi - \chi \bnabla \varphi_s) = \delta^{-1} \sigma, &
\bv = \bzero, &
\bn \cdot \bj_\pm = 0,
\end{array}
\end{equation}
where $\chi$ is the ratio between the dielectric constants of the 
particle and the fluid.

@@

Each discrete variable is located with respect of its cell 
as shown at Figure \ref{fig:grids}.
$\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
using an all-centered grid, whereas $\bV$ is represented by its values at cell 
boundaries, using a staggered grid:
\begin{equation}
\begin{array}{ccccc}
\varPhi^h_{[i,j]} = \varPhi(\bar{r}_i, \bar{\theta}_j), &
C^h_{[i,j]} = C(\bar{r}_i, \bar{\theta}_j), &
P^h_{[i,j]} = P(\bar{r}_i, \bar{\theta}_j). &
V_r^h{}_{[i,j]} = V_r(r_i, \bar{\theta}_j), &
V_\theta^h{}_{[i,j]} = V_\theta(\bar{r}_i, {\theta}_j).
\end{array}
\end{equation}

\begin{figure}[htbp]
    \begin{center}
	\includegraphics[width=1\textwidth]{figs/grids.eps}
        \caption{Computational Grid.}
    \label{fig:grids}
    \end{center}
\end{figure}
